---
title: "Mixed Models for IWQOL"
author: "Olivia Rippee"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, options(digits=3))
library(tidyverse)
library(knitr)
library(lme4)
library(lmerTest)
library(kableExtra)
library(broom.mixed)
library(broom)
library(MASS)
library(pROC)
library(car)
library(fBasics)
```


```{r, data}

data <- read.csv("path/data_OR.csv", 
                 na.strings="NA")

data$treatment_arm <- relevel(factor(data$treatment_arm), ref="In-clinic individual")

data_0mo <- filter(data, time==0)
data_6mo <- filter(data, time==6)
data_24mo <- filter(data, time==24)

predictors <- c("sex", "age", "rurality", "bmi", "mental_health", 
                "two_plus_comorbidities", "treatment_arm", 
                "weight_chng_per", "SITE", "Affiliation")

outcomes <- c("iwqoltotal", "iwqol_delta_0to6", "iwqol_delta_0to24")

data_6mo_na_rm <- drop_na(data_6mo[, names(data) %in% c(predictors, outcomes)])
data_24mo_na_rm <- drop_na(data_24mo[, names(data) %in% c(predictors, outcomes)])

```


# IWQOL at 0 Months

## Univariate Models (IWQOL at 0 Months)

```{r, 0mo univariate}

# Affiliation fixed, site random

# Only affiliation and site
model.affil <- lmer(iwqoltotal ~  Affiliation  + (1 | SITE), data_0mo)
anova.affil <- anova(model.affil, type = "III")
p.affil <- anova.affil[1,6]


# Treatment arm
model.treat <- lmer(iwqoltotal ~  Affiliation + treatment_arm + (1 | SITE), data_0mo)
anova.treat <- anova(model.treat, type = "III")
p.treat <- anova.treat[2,6]
#summary(model.treat)
  # lower QoL in-clinic individual group at baseline


# Age
model.age <- lmer(iwqoltotal ~ Affiliation + age + (1 | SITE), data_0mo)
anova.age <- anova(model.age, type = "III")
p.age <- anova.age[2,6]


# Sex
model.sex <- lmer(iwqoltotal ~ Affiliation + sex + (1 | SITE), data_0mo)
anova.sex <- anova(model.sex, type = "III")
p.sex <- anova.sex[2,6]


# Rurality
model.rural <- lmer(iwqoltotal ~ Affiliation + rurality + (1 | SITE), data_0mo)
anova.rural <- anova(model.rural, type = "III")
p.rural <- anova.rural[2,6]

# bmi (initial)
model.bmi <- lmer(iwqoltotal ~ Affiliation + bmi + (1 | SITE), data_0mo)
anova.bmi <- anova(model.bmi, type = "III")
p.bmi <- anova.bmi[2,6]


# Mental health disorders
model.mental <- lmer(iwqoltotal ~ Affiliation + mental_health + (1 | SITE), data_0mo)
anova.mental <- anova(model.mental, type = "III")
p.mental <- anova.mental[2,6]

# 2+ comorbidities
model.comorbid <- lmer(iwqoltotal ~ Affiliation + two_plus_comorbidities + (1 | SITE), 
                       data_0mo)
anova.comorbid <- anova(model.comorbid, type = "III")
p.comorbid <- anova.comorbid[2,6]

```


```{r, 0mo univariate table}

p.table <- rbind(p.affil, p.treat, p.age, p.sex, p.rural, p.bmi, p.mental, p.comorbid)
colnames(p.table) <- c("p-value")

rownames(p.table) <- c("Affliation", "Treatment Arm", "Age", "Sex", "Rurality", "BMI", 
                       "Mental Health Disorder(s)", "Comorbidities (2+)")

kable(p.table, linesep = "", 
      caption = "Univariate Table - IWQOL Total at 0 Months", 
      col.names = c("Variable", "p-value")) %>%
  kable_styling(latex_options = "striped")

write.csv(p.table, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/0mo_Univariate.csv")

```

## Multivariable Models (IWQOL at 0 Months)

### Full Model

```{r, 0mo full}

# All variables
#-----------------------
model.0mo.full <- lmer(iwqoltotal ~ Affiliation + treatment_arm + age + sex + rurality + 
                         bmi + mental_health + two_plus_comorbidities + (1 | SITE), 
                       data_0mo)

table.0mo.full <- anova(model.0mo.full)

rownames(table.0mo.full) <- c("Affliation", "Treatment Arm", "Age", "Sex", "Rurality", 
                              "BMI", "Mental Health Disorder(s)", "Comorbidities (2+)")

kable(table.0mo.full, linesep = "", 
      caption = "Full Model - IWQOL Total at 0 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.0mo.full, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/0mo_FullModel.csv")

```

\pagebreak

### Reduced Model Intermediates

```{r, 0mo reduced intermediate}

# Remove age
#-----------------------
model.0mo.reduced1 <- lmer(iwqoltotal ~ Affiliation + treatment_arm + sex + rurality + 
                             bmi + mental_health + two_plus_comorbidities + (1 | SITE), 
                           data_0mo)

table.0mo.reduced1 <- anova(model.0mo.reduced1)

rownames(table.0mo.reduced1) <- c("Affliation", "Treatment Arm", "Sex", "Rurality", 
                                  "BMI", "Mental Health Disorder(s)", "Comorbidities (2+)")

kable(table.0mo.reduced1, linesep = "", 
      caption = "Reduced Model 1 - Remove Age - IWQOL Total at 0 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")



# Remove comorbidites
#-----------------------
model.0mo.reduced2 <- lmer(iwqoltotal ~  Affiliation + treatment_arm + sex + rurality +
                             bmi + mental_health + (1 | SITE), data_0mo)

table.0mo.reduced2 <- anova(model.0mo.reduced2)

rownames(table.0mo.reduced2) <- c("Affiliation", "Treatment Arm", "Sex", "Rurality", 
                                  "BMI", "Mental Health Disorder(s)")

kable(table.0mo.reduced2, linesep = "", 
      caption = "Reduced Model 2 - Remove Comorbidities - IWQOL Total at 0 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")



# Remove affiliation
#-----------------------
model.0mo.reduced3 <- lmer(iwqoltotal ~ treatment_arm + sex + rurality + bmi + 
                             mental_health + (1 | SITE), data_0mo)

table.0mo.reduced3 <- anova(model.0mo.reduced3)

rownames(table.0mo.reduced3) <- c("Treatment Arm", "Sex", "Rurality", 
                                  "BMI", "Mental Health Disorder(s)")

kable(table.0mo.reduced3, linesep = "", 
      caption = "Reduced Model 3 - Remove Affiliation - IWQOL Total at 0 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

```

\pagebreak

### Final Model

```{r, 0mo final}

# Remove treatment arm
#-----------------------
model.0mo.reduced4 <- lmer(iwqoltotal ~ sex + rurality + bmi + mental_health + (1 | SITE), 
                           data_0mo)

table.0mo.reduced4 <- anova(model.0mo.reduced4)

rownames(table.0mo.reduced4) <- c("Sex", "Rurality", "BMI", "Mental Health Disorder(s)")

kable(table.0mo.reduced4, linesep = "", 
      caption = "Final Reduced Model - IWQOL Total at 0 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.0mo.reduced4, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/0mo_ReducedModel.csv")

```

### Variance Inflation

```{r, 0mo final vif}

vif.0mo <- data.frame(vif(model.0mo.reduced4))

rownames(vif.0mo) <- c("Sex", "Rurality", "BMI", "Mental Health Disorder(s)")

kable(vif.0mo, linesep = "", 
      caption = "Variance Inflation Factors for the Final Model - IWQOL Total at 0 Months", 
      col.names = c("Variable", "GVIF", "DF", "GVIF^(1/(2*DF))")) %>%
  kable_styling(latex_options = "striped")

write.csv(vif.0mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/0mo_VIF.csv")

```

### Estimates

```{r, 0mo final estimates}

# Estimates and CIs
# ---------------------
beta_estimates_0mo <- data.frame(fixef(model.0mo.reduced4))
colnames(beta_estimates_0mo) <- "Beta Estimate"

CI_bounds_0mo <- data.frame(confint(model.0mo.reduced4))
CI_bounds_0mo <- CI_bounds_0mo[-c(1:2), ]        # Remove ".sig01", ".sigma"
CIs_0mo <- data.frame(apply(CI_bounds_0mo, 1, function(ci) 
  paste0("[", round(ci[1], 2), ", ", round(ci[2], 2), "]")))
colnames(CIs_0mo) <- "95 Percent Confidence Interval"

final_model_results_0mo <- cbind(beta_estimates_0mo, CIs_0mo)

rownames(final_model_results_0mo) <- c("Intercept", "Male", "Large Rural", "Small Rural", 
                                       "BMI", "Mental Health Disorder(s)")

kable(final_model_results_0mo, linesep = "", 
      caption = "Estimates and 95 Percent Confidence Intervals - IWQOL Total at 0 Months") %>%
  kable_styling(latex_options = "striped")

write.csv(final_model_results_0mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/0mo_Estimates.csv")

```


```{r 0mo desc)}

#final_vars <- c("sex", "rurality", "bmi", "mental_health")

sum_sex_mean <- aggregate(data_0mo$iwqoltotal, list(data_0mo$sex), FUN=mean)
sum_sex_sd <- aggregate(data_0mo$iwqoltotal, list(data_0mo$sex), FUN=sd)
sum_sex <- merge(sum_sex_mean, sum_sex_sd, by=c("Group.1"))

sum_rurality_mean <- aggregate(data_0mo$iwqoltotal, 
                               list(data_0mo$rurality), FUN=mean)
sum_rurality_sd <- aggregate(data_0mo$iwqoltotal, 
                             list(data_0mo$rurality), FUN=sd)
sum_rurality <- merge(sum_rurality_mean, sum_rurality_sd, by=c("Group.1"))

sum_mental_health_mean <- aggregate(data_0mo$iwqoltotal, 
                                    list(data_0mo$mental_health), FUN=mean)
sum_mental_health_sd <- aggregate(data_0mo$iwqoltotal, 
                                  list(data_0mo$mental_health), FUN=sd)
sum_mental_health <- merge(sum_mental_health_mean, sum_mental_health_sd, by=c("Group.1"))


sum_table_0mo <- rbind(sum_sex, sum_rurality, sum_mental_health)
colnames(sum_table_0mo) <- c("Variable", "Mean", "Std Deviation")
sum_table_0mo$Variable[6:7] <- c("No Mental Health Disorder", "Mental Health Disorder(s)")
sum_table_0mo <- sum_table_0mo[c(1:3, 5, 4, 6:7), ]


kable(sum_table_0mo, linesep = "", row.names = FALSE, 
      caption = "Variable Summary Table - IWQOL Total at 0 Months") %>%
  kable_styling(latex_options = "striped")

```

\pagebreak


# IWQOL Change 0-6 Months

## Univariate Models (0 to 6 Months)

```{r, 6mo univariate}

# Only affiliation and site
model.affil <- lmer(iwqol_delta_0to6 ~  Affiliation  + (1 | SITE), data_6mo)
anova.affil <- anova(model.affil, type = "III")
p.affil <- anova.affil[1,6]


# Treatment arm
model.treat <- lmer(iwqol_delta_0to6 ~  Affiliation + treatment_arm + (1 | SITE), 
                    data_6mo)
anova.treat <- anova(model.treat, type = "III")
p.treat <- anova.treat[2,6]


# Age
model.age <- lmer(iwqol_delta_0to6 ~ Affiliation + age + (1 | SITE), data_6mo)
anova.age <- anova(model.age, type = "III")
p.age <- anova.age[2,6]


# Sex
model.sex <- lmer(iwqol_delta_0to6 ~ Affiliation + sex + (1 | SITE), data_6mo)
anova.sex <- anova(model.sex, type = "III")
p.sex <- anova.sex[2,6]


# Rurality
model.rural <- lmer(iwqol_delta_0to6 ~ Affiliation + rurality + (1 | SITE), 
                    data_6mo)
anova.rural <- anova(model.rural, type = "III")
p.rural <- anova.rural[2,6]


# bmi (initial)
model.bmi <- lmer(iwqol_delta_0to6 ~ Affiliation + bmi + (1 | SITE), data_6mo)
anova.bmi <- anova(model.bmi, type = "III")
p.bmi <- anova.bmi[2,6]


# Mental health disorders
model.mental <- lmer(iwqol_delta_0to6 ~ Affiliation + mental_health + (1 | SITE), 
                     data_6mo)
anova.mental <- anova(model.mental, type = "III")
p.mental <- anova.mental[2,6]


# 2+ comorbidities
model.comorbid <- lmer(iwqol_delta_0to6 ~ Affiliation + two_plus_comorbidities 
                       + (1 | SITE), data_6mo)
anova.comorbid <- anova(model.comorbid, type = "III")
p.comorbid <- anova.comorbid[2,6]


# Percent Weight Change
model.weight <- lmer(iwqol_delta_0to6 ~  Affiliation + weight_chng_per 
                     + (1 | SITE), data_6mo)
anova.weight <- anova(model.weight, type = "III")
p.weight <- anova.weight[2,6]

```


```{r, 6mo univariate table}

p.table <- rbind(p.affil, p.treat, p.age, p.sex, p.rural, p.bmi, 
                 p.mental, p.comorbid, p.weight)
colnames(p.table) <- c("p-value")

rownames(p.table) <- c("Affliation", "Treatment Arm", "Age", "Sex", "Rurality", "BMI", 
                       "Mental Health Disorder(s)", "Comorbidities (2+)", 
                       "Percent Weight Change")

kable(p.table, linesep = "", caption = "Univariate Table - Change in IWQOL at 6 Months", 
      col.names = c("Variable", "p-value")) %>%
  kable_styling(latex_options = "striped")

write.csv(p.table, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/6mo_Univariate.csv")

```

## Multivariable Models (0 to 6 Months)

### Full Model

```{r, 6mo full}

# All variables
# -----------------------
model.6mo.full <- lmer(iwqol_delta_0to6 ~ age + sex + mental_health + weight_chng_per 
                       + (1 | SITE), data_6mo)

table.6mo.full <- anova(model.6mo.full)

rownames(table.6mo.full) <- c("Age", "Sex", "Mental Health Disorder(s)", 
                              "Percent Weight Change")

kable(table.6mo.full, linesep = "", 
      caption = "Full Model - Change in IWQOL at 6 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.6mo.full, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/6mo_FullModel.csv")

```

### Final Model

```{r, 6mo final}

# Remove comorbidities
# -----------------------
model.6mo.reduced1 <- lmer(iwqol_delta_0to6 ~ sex + mental_health + weight_chng_per 
                           + (1 | SITE), data_6mo)

table.6mo.reduced1 <- anova(model.6mo.reduced1)

rownames(table.6mo.reduced1) <- c("Sex", "Mental Health Disorder(s)", "Percent Weight Change")

kable(table.6mo.reduced1, linesep = "", 
      caption = "Final Reduced Model - Change in IWQOL at 6 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.6mo.reduced1, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/6mo_ReducedModel.csv")

```

\pagebreak

### Variance Inflation

```{r, 6mo final vif}

vif.6mo <- data.frame(vif(model.6mo.reduced1))
rownames(vif.6mo) <- c("Sex", "Mental Health Disorder(s)", "Percent Weight Change")
colnames(vif.6mo) <- "VIF"

kable(vif.6mo, linesep = "", 
      caption = "Variance Inflation Factors for the Final Model - Change in IWQOL at 6 Months", 
      col.names = c("Variable", "VIF")) %>%
  kable_styling(latex_options = "striped")

write.csv(vif.6mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/6mo_VIF.csv")

```

### Estimates

```{r, 6mo final estimates}

# Estimates and CIs
# ---------------------
beta_estimates_6mo <- data.frame(fixef(model.6mo.reduced1))
colnames(beta_estimates_6mo) <- "Beta Estimate"

CI_bounds_6mo <- data.frame(confint(model.6mo.reduced1))
CI_bounds_6mo <- CI_bounds_6mo[-c(1:2), ]        # Remove ".sig01", ".sigma"
CIs_6mo <- data.frame(apply(CI_bounds_6mo, 1, function(ci) 
  paste0("[", round(ci[1], 2), ", ", round(ci[2], 2), "]")))
colnames(CIs_6mo) <- "95 Percent Confidence Interval"

final_model_results_6mo <- cbind(beta_estimates_6mo, CIs_6mo)

rownames(final_model_results_6mo) <- c("Intercept", "Male", "Mental Health Disorder(s)", 
                                       "Percent Weight Change")

kable(final_model_results_6mo, linesep = "", 
      caption = "Estimates and 95 Percent Confidence Intervals - Change in IWQOL at 6 Months",
      col.names = c("Variable", "Beta Estimate", "95 Percent Confidence Interval")) %>%
  kable_styling(latex_options = "striped")

write.csv(final_model_results_6mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/6mo_Estimates.csv")

```


```{r 6mo desc}

#final_vars <- c("sex", "mental_health", "weight_chng_per")

sum_sex_mean <- aggregate(data_6mo_na_rm$iwqol_delta_0to6, 
                          list(data_6mo_na_rm$sex), FUN=mean)
sum_sex_sd <- aggregate(data_6mo_na_rm$iwqol_delta_0to6, 
                        list(data_6mo_na_rm$sex), FUN=sd)
sum_sex <- merge(sum_sex_mean, sum_sex_sd, by=c("Group.1"))


sum_mental_health_mean <- aggregate(data_6mo_na_rm$iwqol_delta_0to6, 
                                    list(data_6mo_na_rm$mental_health), FUN=mean)
sum_mental_health_sd <- aggregate(data_6mo_na_rm$iwqol_delta_0to6, 
                                 list(data_6mo_na_rm$mental_health), FUN=sd)
sum_mental_health <- merge(sum_mental_health_mean, sum_mental_health_sd, by=c("Group.1"))


sum_table_6mo <- rbind(sum_sex, sum_mental_health)
colnames(sum_table_6mo) <- c("Variable", "Mean", "Std Deviation")
sum_table_6mo$Variable[3:4] <- c("No Mental Health Disorder", "Mental Health Disorder(s)")

kable(sum_table_6mo, linesep = "", row.names = FALSE, 
      caption = "Variable Summary Table - Change in IWQOL at 6 Months") %>%
  kable_styling(latex_options = "striped")

```

\pagebreak


# IWQOL Change 0-24 Months

## Univariate Models (0-24 Months)

```{r, 24mo univariate}

# Only affiliation and site
model.affil <- lmer(iwqol_delta_0to24 ~  Affiliation  + (1 | SITE), data_24mo)
anova.affil <- anova(model.affil, type = "III")
p.affil <- anova.affil[1,6]


# Treatment arm
model.treat <- lmer(iwqol_delta_0to24 ~  Affiliation + treatment_arm 
                    + (1 | SITE), data_24mo)
anova.treat <- anova(model.treat, type = "III")
p.treat <- anova.treat[2,6]
#summary(model.treat)


# Age
model.age <- lmer(iwqol_delta_0to24 ~ Affiliation + age + (1 | SITE), data_24mo)
anova.age <- anova(model.age, type = "III")
p.age <- anova.age[2,6]


# Sex
model.sex <- lmer(iwqol_delta_0to24 ~ Affiliation + sex + (1 | SITE), data_24mo)
anova.sex <- anova(model.sex, type = "III")
p.sex <- anova.sex[2,6]


# Rurality
model.rural <- lmer(iwqol_delta_0to24 ~ Affiliation + rurality + (1 | SITE), data_24mo)
anova.rural <- anova(model.rural, type = "III")
p.rural <- anova.rural[2,6]


# bmi (initial)
model.bmi <- lmer(iwqol_delta_0to24 ~ Affiliation + bmi + (1 | SITE), data_24mo)
anova.bmi <- anova(model.bmi, type = "III")
p.bmi <- anova.bmi[2,6]


# Mental health disorders
model.mental <- lmer(iwqol_delta_0to24 ~ Affiliation + mental_health 
                     + (1 | SITE), data_24mo)
anova.mental <- anova(model.mental, type = "III")
p.mental <- anova.mental[2,6]

# 2+ comorbidities
model.comorbid <- lmer(iwqol_delta_0to24 ~ Affiliation + two_plus_comorbidities 
                       + (1 | SITE), data_24mo)
anova.comorbid <- anova(model.comorbid, type = "III")
p.comorbid <- anova.comorbid[2,6]


# Percent Weight Change
model.weight <- lmer(iwqol_delta_0to6 ~  Affiliation + weight_chng_per 
                     + (1 | SITE), data_24mo)
anova.weight <- anova(model.weight, type = "III")
p.weight <- anova.weight[2,6]

```


```{r, 24mo univariate table}

p.table <- rbind(p.affil, p.treat, p.age, p.sex, p.rural, 
                 p.bmi, p.mental, p.comorbid, p.weight)
colnames(p.table) <- c("p-value")

rownames(p.table) <- c("Affliation", "Treatment Arm", "Age", "Sex", "Rurality", "BMI", 
                       "Mental Health Disorder(s)", "Comorbidities (2+)", 
                       "Percent Weight Change")

kable(p.table, linesep = "", 
      caption = "Univariate Table - Change in IWQOL at 24 Months", 
      col.names = c("Variable", "p-value")) %>%
  kable_styling(latex_options = "striped")

write.csv(p.table, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/24mo_Univariate.csv")

```


## Multivariable Models (0-24 Months)

### Full Model

```{r, 24mo full}

# Full model
# ---------------------
model.24mo.full <- lmer(iwqol_delta_0to24 ~ age + sex + mental_health + weight_chng_per 
                        + (1 | SITE), data_24mo)

table.24mo.full <- anova(model.24mo.full)

rownames(table.24mo.full) <- c("Age", "Sex", "Mental Health Disorder(s)", 
                               "Percent Weight Change")

kable(table.24mo.full, linesep = "", 
      caption = "Full Model - Change in IWQOL at 24 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.24mo.full, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/24mo_FullModel.csv")

```

### Final Model

```{r, 24mo final}

# Remove age
# ---------------------
model.24mo.reduced1 <- lmer(iwqol_delta_0to24 ~ sex + mental_health + weight_chng_per 
                            + (1 | SITE), data_24mo)

table.24mo.reduced1 <- anova(model.24mo.reduced1)

rownames(table.24mo.reduced1) <- c("Sex", "Mental Health Disorder(s)", 
                                   "Percent Weight Change")

kable(table.24mo.reduced1, linesep = "", 
      caption = "Final Reduced Model - Change in IWQOL at 24 Months", 
      col.names = c("Variable", "Sum Sq", "Mean Sq", "Num DF", 
                    "Den DF", "F value", "Pr(>F)")) %>%
  kable_styling(latex_options = "striped")

write.csv(table.24mo.reduced1, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/24mo_ReducedModel.csv")

```

\pagebreak

### Variance Inflation

```{r, 24mo final vif}

vif.24mo <- data.frame(vif(model.24mo.reduced1))

rownames(vif.24mo) <- c("Sex", "Mental Health Disorder(s)", "Percent Weight Change")
colnames(vif.24mo) <- "VIF"

kable(vif.24mo, linesep = "", 
      caption = "Variance Inflation Factors for the Final Model - Change in IWQOL at 24 Months", 
      col.names = c("Variable", "VIF")) %>%
  kable_styling(latex_options = "striped")

write.csv(vif.24mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/24mo_VIF.csv")

```

### Estimates

```{r, 24mo final estimates}

# Estimates and CIs
# ---------------------
beta_estimates_24mo <- data.frame(fixef(model.24mo.reduced1))
colnames(beta_estimates_24mo) <- "Beta Estimate"

CI_bounds_24mo <- data.frame(confint(model.24mo.reduced1))
CI_bounds_24mo <- CI_bounds_24mo[-c(1:2), ]        # Remove ".sig01", ".sigma"
CIs_24mo <- data.frame(apply(CI_bounds_24mo, 1, function(ci) 
  paste0("[", round(ci[1], 2), ", ", round(ci[2], 2), "]")))
colnames(CIs_24mo) <- "95 Percent Confidence Interval"

final_model_results_24mo <- cbind(beta_estimates_24mo, CIs_24mo)

rownames(final_model_results_24mo) <- c("Intercept", "Male", "Mental Health Disorder(s)", 
                                        "Percent Weight Change")

kable(final_model_results_24mo, linesep = "", 
      caption = "Estimates and 95 Percent Confidence Intervals - Change in IWQOL at 24 Months", 
      col.names = c("Variable", "Beta Estimate", "95 Percent Confidence Interval")) %>%
  kable_styling(latex_options = "striped")

write.csv(final_model_results_24mo, 
          "S:/Biostats/BIO-STAT/Brown_Lexie/BIOS898/Olivia/Output Tables/24mo_Estimates.csv")

```


```{r 24mo desc}

#final_vars <- c("sex","household_income", "mental_health", "weight_chng_per")

sum_sex_mean <- aggregate(data_24mo_na_rm$iwqol_delta_0to24, 
                          list(data_24mo_na_rm$sex), FUN=mean)
sum_sex_sd <- aggregate(data_24mo_na_rm$iwqol_delta_0to24, 
                        list(data_24mo_na_rm$sex), FUN=sd)
sum_sex <- merge(sum_sex_mean, sum_sex_sd, by=c("Group.1"))

sum_mental_health_mean <- aggregate(data_24mo_na_rm$iwqol_delta_0to6, 
                                    list(data_24mo_na_rm$mental_health), FUN=mean)
sum_mental_health_sd <- aggregate(data_24mo_na_rm$iwqol_delta_0to6, 
                                 list(data_24mo_na_rm$mental_health), FUN=sd)
sum_mental_health <- merge(sum_mental_health_mean, sum_mental_health_sd, by=c("Group.1"))

sum_table_24mo <- rbind(sum_sex, sum_mental_health)
colnames(sum_table_24mo) <- c("Variable", "Mean", "Std Deviation")
sum_table_24mo$Variable[3:4] <- c("No Mental Health Disorder", "Mental Health Disorder(s)")

kable(sum_table_24mo, linesep = "", row.names = FALSE, 
      caption = "Variable Summary Table - Change in IWQOL at 24 Months") %>%
  kable_styling(latex_options = "striped")

```

